---
title: Professional Development
output: 
  html_document:
    toc_depth: 3
---

```{r load libraries, include=FALSE, echo = FALSE}
library(tidyverse)
library(kableExtra )
```

# Funding Applications 


```{r funding applications, echo = FALSE}
funding_applications = read.csv("./funding_applications.csv")
funding_applications %>% knitr::kable(caption = "Status of all funding applications to date.") %>% kable_styling()
```



# Presentations 

```{r presentation, echo = FALSE}
presentations = read.csv("./presentations.csv")
presentations %>% knitr::kable(caption = "Presentations to date.") %>% kable_styling()

```


# Mentorship 

**University of Georgia (2018 - Present)**
Mentored for UGA Undergraduate Academic Research (Dpt. Environmental Health Sciences) and for UGA CURO Assistantship

**University of North Carolina at Chapel Hill (2017 - 2018)**
Graduate Student Mentor, Environmental Health Microbiology Laboratory
Trained seven undergraduate students in environmental microbiology, mentored for UNC Undergraduate Academic Research (Dpt. of Biology, Dpt. of Chemistry), for UNC Honors Research, and for UNC Summer Undergraduate Research Fellowship

# Committees 

College of Public Health Course Approval Committee (2019 - 2020)
